---
title: "R Notebook"
output: html_notebook
---

---
title: "VC_Trends"
author: "Paul Rode"
date: "1/6/2022"
output: html_document


```{r, echo = FALSE, message = FALSE, warning = FALSE}

###############################################################################
#                             Set up environment                                #
###############################################################################

my_packages <- c("tidyverse", "vroom" , "janitor" , "glue" ,  "tsibble" , "tidytext","lubridate", "fable", "tsibbledata", "ggplot2", "forecast", "tseries", "rio", "zoo", "readxl", "tsibbledata", "knitr", "kableExtra", "formattable") 
invisible( lapply(my_packages, require, character.only = TRUE))

#Choose one working site:
place <- "Home"
# place <-  "work"


#Set proper working Dir 
if (place == "Home"){setwd("C:/Users/paulr/Documents/R/200Park_VC")} else
{setwd("C:/Users/prode/Documents/R/200Park_VC")}

# Check for data directory and if one is not present then make it
if (!file.exists("data")) {
  dir.create("data")}
  
# Set up the not in operator 
  `%!in%` <- Negate(`%in%`)

rm(place, my_packages )
  
```

The goal with this data project is to use the LL84 benchmarking to
identify the thermal potential in each of the building typologies. 1.
Identify the kBTU's of gas, oil and district steam used (thermal fuel)
in the commercial stock. 2. Allocate the thermal fuel among building
typologies. 3. Show ranking of typologies by sf and thermal fule volumn.
3. Show steam in manhattan as a breakout.

Data wranging actions taken
1. eliminated duplicates.
2. Deleted outliers using a simple strategy of deteating the top ten and bottom ten buildings by steam consumption.  See 65 Broadway for why this is necessary, the steam consumption value was orders of magnitude higher then possible. 

Note that while Local Law 84 data estist back to 2010 data fields before 2015 lack specific energy consumption and year built. 

```{r echo=FALSE, message=FALSE, warning=FALSE}


# Read in data 

Center <- read_excel("data/visitors center 2022-01-05 15_16_30 -0500.xlsx", sheet = "DATA", col_names = c("Date", "Temp F", "RH", "DewPt"), na = "NA", col_types = c("skip", "date", "numeric", "numeric", "numeric" )) %>% na.omit()

plot(Center)
ggplot(data = Center, aes(x = Date, y = `Temp F`)) +
  geom_point() +
  geom_point(aes(x = Date, y = RH, color = 2))



################################################################################
L84 %>%
  group_by(Data, Type) %>%
  summarise( GSF = sum(GSF), Buildings = sum(No.Buildings)) -> Type_tables
 Type_tables %>% group_by(Data) %>% summarise(Type = n(), "Number of Buildings" = sum(Buildings), "Footage" = sum(GSF)) -> Table1

kable(Table1, col.names = c("Year", "Property Use Types", "Buildings", "SqFt"), align = "cccc", caption = "Table 1 - Datasets property types quantities and areas") -> Table1

Table1


################################################################################


```
